Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-05-05 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
hot, cool slope sections in intro; still unsure about scope relative to P1

@@

	\par \citet{cargill_implications_1994} and \citet{cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component and thus a steep hotward slope, the so-called ``smoking gun'' of nanoflare heating. Unfortunately, observing this high-temperature emission is difficult and in some cases impossible. The reason for this difficulty is twofold. First, thermal conduction is a very efficient cooling mechanism at high temperatures and large spatial temperature gradients. When a loop is heated impulsively, its temperature rises quickly while the increase in density lags behind. By the time the density has increased sufficiently (due to chromospheric evaporation brought about by the response of the transition region to the strong downward coronal heat flux) to allow for an appreciable amount of emission (recalling $\mathrm{EM}\propto n^2$), thermal conduction has cooled the loop far below its initial hot temperature, making a direct detection of $\sim10$ MK plasma very difficult.

@@

	\par The second reason for this difficulty is non-equilibrium ionization (NEI). It is usually assumed that the observed emission lines, because of their known formation temperatures, are a direct indicator of the plasma temperature. However, if the heating (or cooling) timescale is shorter than the ionization equilibration timescale, the time it takes for the ion population to settle into the assumed charge state, an equilibrium assumption can lead to a misdiagnosis of the plasma temperature. This makes signatures of hot, nanoflare-heated plasma especially difficult to detect if the high temperatures persist for less than the ionization timescale \citep{bradshaw_explosive_2006,bradshaw_what_2011,reale_nonequilibrium_2008}.

@@

	\par Several workers have modeled both steady and impulsive heating in coronal loops. 

@@

	\par Despite these difficulties, various attempts have been made to observe this faint high-temperature emission. Using the broadband X-Ray Telescope (XRT) \citep{golub_x-ray_2007} on board the \textit{Hinode} spacecraft \citep{kosugi_hinode_2007}, \citet{schmelz_hinode_2009} and \citet{reale_evidence_2009} show a faint hot component in the reconstructed $\mathrm{DEM}$ curves. However, since the channels on such broadband instruments can often be polluted by low-temperature emission, the reliability of such measurements depends on the filtering technique used. Additionally, \citet{winebarger_defining_2012} showed that combinations of measurements from XRT and the Extreme-ultraviolet Imaging Spectrometer (EIS) \citep{culhane_euv_2007}, also on  \textit{Hinode}, leave a ``blind spot'' in the $\mathrm{EM}-T$ space conincident with the range where evidence for nanoflare heating is likely to be found. 

@@

	\par Unambiguous observational evidence of nanoflare heating must come from pure spectroscopic measurements \citep[see][]{brosius_pervasive_2014}. Additionally, new instruments with higher spatial and temporal resolution, such as \textit{IRIS} \citep{de_pontieu_interface_2014} and the \textit{Hi-C} sounding rocket \citep{cirtain_energy_2013} have provided encouraging results for impulsive heating \citep{testa_observing_2013,testa_evidence_2014}. Future missions like the Marshall Grazing Incidence X-ray Spectrometer (MaGIXS) \citep{kobayashi_marshall_2011,winebarger_new_2014}, with a wavelength range of 6-24 \ang and a temperature range of $6.2<\log{T}<7.2$, aim to probe this previously poorly-resolved portion of the coronal spectrum in hopes of better quantifying the presence of faint, high-temperature plasma.

@@

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release. Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating. In the case of high-frequency heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_c$, where $\tau_c$ is the loop cooling time, and in the case of low-frequency heating $t_N\gg\tau_c$. Steady heating is just high-frequency heating in the limit $t_N\to0$.
	\par One strategy for constraining the nanoflare model is analysis of modeled and observed emission measure distributions for signatures of impulsive heating in active region (AR) cores. As with cool emission, hot emission is also often described by a power-law relation of the form $\mathrm{EM}\propto T^{-b}$. Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $6.6\lesssim\log{T}\lesssim7.2$. However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range. \citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of ARs. All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit.
	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares. In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting emission measure distribution. In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution versus uniform heating rates. Additionally, we consider the effect of scaling the inter-event waiting time to the event energy and how NEI may affect hot emission measure slopes. We use an emission measure ratio, similar to that of \citet{brosius_pervasive_2014} to assess the relative importance of hot emission over the entire range of power-law indices and heating frequencies. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure curves and slopes for the electron and ion heating cases \st{as well as the equivalent single-fluid cases}. In \autoref{sec:discussion}, we discuss the implications of two-fluid effects in the context of hot \st{and cool} emission measure slopes and the nanoflare heating model. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

>>>>

	\shorttitle{``Hot'' Non-flaring Plasmas II. Nanoflare Trains}

@@

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release. Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating. In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}. Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$. \hl{Discuss past heating frequency studies}

@@

	\par One strategy for constraining potential heating models is analysis of modeled and observed emission measure distributions in active region (AR) cores. Originally proposed by \citet{jordan_structure_1975}, it is well-known that the emission measure, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$, scales as $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, where $T_m$ is the temperature at which $\mathrm{EM}(T)$ peaks. Observations have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}. 

@@

	\par Hydrodynamic models of nanoflare-heated loops have found similar results when calculating emission measure slopes. While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$. \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the observed emission measure slopes be found. This is consistent with the findings of \citet{ugarte-urra_determining_2014} who estimated an inter-event period of 1400 s using an event detection algorithm on filtered SDO/AIA 94 \ang images of AR cores. \hl{Steady-heating counter arguments?}

@@

	\par\hl{Hot slope calculations, predictions} A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$. Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim\log{T}\lesssim7.2$. However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of ARs. All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit. \hl{more refs here? Summarize in a sentence or two and provide many refs, don't want to repeat paper 1}

@@

	\par \citet{cargill_implications_1994,cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component and thus a steep hotward slope, the so-called ``smoking gun'' of nanoflare heating. Unfortunately, observing this high-temperature emission is difficult and in some cases impossible. The reason for this difficulty is twofold. First, thermal conduction is a very efficient cooling mechanism at high temperatures and large spatial temperature gradients. When a loop is heated impulsively, its temperature rises quickly while the increase in density lags behind. By the time the density has increased sufficiently (due to chromospheric evaporation brought about by the response of the transition region to the strong downward coronal heat flux) to allow for an appreciable amount of emission (recalling $\mathrm{EM}\propto n^2$), thermal conduction has cooled the loop far below its initial hot temperature, making a direct detection of $\sim10$ MK plasma very difficult.

@@

	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares. We found that emission signatures of the heating are likely to be found in the temperature range $4\lesssim T\lesssim 10$ MK. In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting emission measure distribution. In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution versus uniform heating rates. Additionally, we consider the effect of scaling the inter-event waiting time to the event energy and how NEI may affect hot emission measure slopes. We use an emission measure ratio, similar to that of \citet{brosius_pervasive_2014} to assess the relative importance of hot emission over the entire range of power-law indices and heating frequencies. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure curves and slopes for the electron and ion heating cases \st{as well as the equivalent single-fluid cases}. In \autoref{sec:discussion}, we discuss the implications of two-fluid effects in the context of hot \st{and cool} emission measure slopes and the nanoflare heating model. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.
